### 2019-04-04 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Using \begin{framed}...\end{framed} for all algorithms.
Moved a lot of appendix in main text for Chapter 5. See #15

% -----------------------------------------------------------------
\section{Regret Decompositions}
\label{app:5:regretdec}

% -----------------------------------------------------------------
\subsection{Proof of Lemma~\ref{lem:5:DecompositionRegret}}
\label{proof:5:DecompositionRegret}

    Using the definition of regret $R_T$ from \eqref{eq:5:regret}, and this collision indicator $\eta^j(t):=\indic(\overline{C^j(t)})$,
    \begin{align*}
      R(T)
      &= \left(\sum_{k=1}^{M}\mu_k^*\right)T - \E_{\mu}\left[\sum_{t=1}^T\sum_{j=1}^M Y_{A^j(t),t} \eta^j(t) \right]
       = \left(\sum_{k=1}^{M}\mu_k^*\right)T - \E_{\mu}\left[\sum_{t=1}^T\sum_{j=1}^M \mu_{A^j(t)} \eta^j(t)\right]
      \shortintertext{The last equality comes from the linearity of expectations, and the fact that $\E_{\mu}[Y_{k,t}] = \mu_k$ (for all $t$, from the \iid{} hypothesis), and the independence from $A^j(t)$, $\eta^j(t)$ and $Y_{k,t}$ (observed \emph{after} playing $A^j(t)$). So $\E_{\mu}[Y_{A^j(t),t} \eta^j(t)] = \sum_{k} \E_{\mu}[\mu_k \indic(A^j(t),t) \eta^j(t)] = \E_{\mu}[\mu_{A^j(t)} \eta^j(t)]$. And so}
      R(T)
      &= \E_{\mu}\left[ \sum_{t=1}^{T}\sum_{j \in \Mbest} \mu_j
        - \sum_{t=1}^{T} \sum_{j=1}^{M} \mu_{A^j(t)} \eta^j(t) \right] \\
        % &= \underbrace{\left( \frac{1}{M} \sum_{j \in \Mbest} \mu_j \right)}_{:= \overline{\mu}^*} (T M)
      &= \left( \frac{1}{M} \sum_{j \in \Mbest} \mu_j \right)
        - \sum_{k=1}^{K} \sum_{j=1}^{M} \mu_k \E_{\mu}\left[ T^j_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
      \shortintertext{For the first term, we have $T M = \sum\limits_{k=1}^{K} \sum\limits_{j=1}^{M} \E_{\mu}\left[ T^j_k(T)\right]$, and if we denote $\overline{\mu}^* := \frac{1}{M} \sum\limits_{j \in \Mbest} \mu_j$ the average mean of the $M$-best arms, then,}
      &= \sum_{k=1}^{K} \sum_{j=1}^{M} (\overline{\mu}^* - \mu_k) \E_{\mu}\left[ T^j_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
      \shortintertext{Let $\overline{\Delta_k} := \overline{\mu}^* - \mu_k$ be the gap between the mean of the arm $k$ and the $M$-best average mean, and if $M^*$ denotes the index of the worst of the $M$-best arms (\ie, $M^* = \arg\min_{k\in\Mbest}(\mu_k)$), then by splitting $\{1,\dots,K\}$ into three disjoint sets $\Mbest \cupdot \Mworst = (\Mbest\setminus\{M^*\}) \cupdot \{M^*\} \cupdot \Mworst$, we get}
      &= \sum_{k \in \Mbest\setminus\{M\}} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]
        + \overline{\Delta_{M^*}} \E_{\mu}\left[ T_{M^*}(T) \right] \\
        &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
      \shortintertext{But for $k = M^*$, $T_{M^*}(T) = T M^* - \sum\limits_{k \in \Mbest\setminus\{M\}} \E_{\mu}\left[ T_k(T) \right] - \sum\limits_{k \in \Mworst} \E_{\mu}\left[ T_k(T) \right]$, so by recombining the terms, we obtain,}
      &= \sum_{k \in \Mbest\setminus\{M\}} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]
        + \overline{\Delta_{M^*}} T M^* \\
        &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
    \end{align*}
    The term $\overline{\Delta_k} - \overline{\Delta_{M^*}}$ simplifies to $\mu_{M^*} - \mu_k$, and so $\overline{\Delta_{M^*}} = \frac{1}{M} \sum_{k=1}^{M} \mu_k - \mu_{M^*}$ by definition of $\overline{\mu}^*$. And for $k=M^*$, $\mu_{M^*} - \mu_k = 0$, so the first sum can be written for $k = 1,\dots,M$ only, so
    % \vspace*{5pt}
    \begin{align*}
      R(T)
      &= \sum_{k \in \Mbest} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
        + \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) T \\
        &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right]
    \end{align*}
    And so we obtain the decomposition with three terms \ref{eq:5:term1}, \ref{eq:5:term2} and \ref{eq:5:term3}.
    \begin{align*}
    R(T)
      &= \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) \left(T - \E_{\mu}\left[ T_k(T) \right]\right)
        + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
        + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
    \end{align*}
    % Which is exactly the decomposition we wanted to prove.

% -----------------------------------------------------------------
\subsection{Proof of Lemma~\ref{lem:5:1stLowerBound}}
\label{proof:5:1stLowerBound}

  Note that term \ref{eq:5:term3} is clearly lower bounded by $0$
  but it is not obvious for \ref{eq:5:term2} as there is no reason for $T_k(T)$ to be upper bounded by $T$.
  %
  Let $T_k^{!}(T) := \sum_{t=1}^{T} \indic(\exists! j, A^j(t)=k)$,
  where the notation $\exists!$ stands for ``there exists a unique''.
  Then $T_k(T) = \sum_{t=1}^{T} \sum_{j=1}^{M} \indic(A^j(t) = k)$ can be decomposed as
  \begin{equation*}
    T_k(T) = \sum_{t=1}^{T} \indic(\exists! j, A^j(t) = k) + \sum_{t=1}^{T} \sum_{j=1}^{M} c_{k,t} \indic(A^j(t) = k)
    = T_k^{!}(T) + C_k(T).
  \end{equation*}
  By focusing on the two terms $\ref{eq:5:term2} + \ref{eq:5:term3}$ from the decomposition of $R_T(\boldsymbol{\mu}, M, \rho)$ from Lemma~\ref{lem:5:DecompositionRegret}, we have
  \begin{align*}
    \ref{eq:5:term2} + \ref{eq:5:term3} &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)] \\
    & \;\;\;\;\;\; + \sum_{k=1}^{M} \mu_k \E_{\mu}[C_k(T)]
    - \sum_{k \in \Mbest} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)]
    + \sum_{k \in \Mworst} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k=1}^{M} \min(\mu_M^*, \mu_k) \E_{\mu}[C_k(T)].
  \end{align*}
  And now both terms are non-negative, as $T_k^!(T) \leq T$, $\min(\mu_M^*, \mu_k)\geq 0$, and $C_k(T) \geq 0$, so $\ref{eq:5:term2} + \ref{eq:5:term3} \geq 0$
  which proves that $R_T(\boldsymbol{\mu}, M, \rho) \geq \ref{eq:5:term1}$, as wanted.

% -----------------------------------------------------------------
\subsection{Proof of Lemma~\ref{lem:5:1stUpperBound}}
\label{proof:5:1stUpperBound}

Recall that we want to upper bound
$ (b) : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[T_k(T)]\right)$.
First, we observe that, for all $k\in \Mbest$,
\begin{eqnarray*}
  T - \E_{\mu}[T_k(T)] & \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] \\
  & = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],
\end{eqnarray*}
where we denote by $\widehat{S}_t = \{A^j(t), j \in \{1,\dots,M\}\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
\begin{eqnarray*}
 (b) & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[T_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
 & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
\end{eqnarray*}
The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
\[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
which yields
\[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[T_k(T)\right]\]
and Lemma~\ref{lem:5:1stUpperBound} follows.

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{The \RandTopM{} algorithm}
\label{app:5:RandTopM}

\TODOL{I should include this in the main text, it makes more sense to present RandTopM and then MCTopM !}

We now state precisely the \RandTopM{} algorithm below in Algorithm~\ref{algo:5:RandTopM} (page \pageref{algo:5:RandTopM}).
It is essentially the same algorithm as \MCTopM,
but in a simpler version as the ``Chair'' aspect is removed, that is, there is no notion of state $s^j(t)$ (\cf{} Algorithm~\ref{algo:5:MCTopM}).
%
Player $j$ is always considered ``not fixed'',
and a \emph{collision always forces a uniform sampling of the next arm} from $\TopM(t)$
in the case of \RandTopM.

\vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      % \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $\{1,\dots,K\}$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(1) \sim \cU(\{1,\dots,K\})$ and $C^j(1)=\mathrm{False}$ \\
              \For{$t = 0, \dots, T - 1$}{
                  %
                  \eIf{$A^j(t) \notin \TopM(t)$}{
                    \eIf(\tcp*[f]{collision}){$C^j(t)$}{
                      $A^j(t+1) \sim \cU \left(\TopM(t)\right)$
                      \tcp*[f]{randomly switch}
                      }(\tcp*[f]{randomly switch on an arm that had smaller UCB at $t-1$}){
                        $A^j(t+1) \sim \cU \left(\TopM(t) \cap \left\{k : g_k^j(t-1) \leq g^j_{A^j(t)}(t-1)\right\}\right)$
                      }
                    }{
                      $A^j(t+1) = A^j(t)$
                      \tcp*[f]{stays on the same arm}
                    }
                  Play arm $A^j(t+1)$, get new observations (sensing and collision), \\
                  Compute the indices $g^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \RandTopM{} decentralized learning policy]{The \RandTopM{} decentralized learning policy (for a fixed underlying index policy $g^j$).}
          \label{algo:5:RandTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      % \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
\vspace*{-5pt}  % XXX remove if problem

@@

Using \eqref{eq:5:KeyInclusion}, one can then upper bound the number of selections of arm $k$ by user $j$ up to round $T$ as
\begin{align*}
\E_{\mu}[T_k^j(T)]
&= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
= \sum_{t=1}^T \Pr\left( A^j(t) = k \right).\\
%&= \sum_{t=1}^T \Pr\left( A^j(t) = k,\;\; \exists m \in\Mbest,\; g_m(t) < g_k(t) \right) \\
&= \sum_{t=1}^T \Pr\left( A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}^j(t) < g_k^j(t) \right).
%
\shortintertext{Considering the relative position of the upper-confidence bound $g_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition}
\E_{\mu}[T_k^j(T)] &\leq \sum_{t=1}^T\Pr\left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}(t) \leq g_k(t) , \forall m \in \{1,\dots,M\}: \;  g_{m^*}(t) \geq \mu_m^* \right)\\
&\;\;\;\;\;\;\;\; + \sum_{t=1}^T\Pr\left( \exists m \in\{1,\dots,M\}: \; g_{m^*}(t) < \mu_m^* \right) \\
&\leq \sum_{t=1}^T\Pr\left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; \mu_{m}^* \leq g_k(t)\right)+ \sum_{m=1}^M\sum_{t=1}^T\Pr\left(g_{m^*}(t) < \mu_m^* \right) \\
%
&\leq
\sum_{t=1}^T
  \Pr\left( A^j(t) = k,\; \mu_{M^*} \leq g_k(t) \right)
+
\sum_{m=1}^M
  \sum_{t=1}^T \Pr\left( g_{m^*}(t) < \mu_m^* \right),
\end{align*}
where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in \{1, \dots,M\}$.

>>>>

% % -----------------------------------------------------------------
% \section{Regret Decompositions}
% \label{app:5:regretdec}

% % -----------------------------------------------------------------
% \subsection{Proof of Lemma~\ref{lem:5:DecompositionRegret}}
% \label{proof:5:DecompositionRegret}

%     Using the definition of regret $R_T$ from \eqref{eq:5:regret}, and this collision indicator $\eta^j(t):=\indic(\overline{C^j(t)})$,
%     \begin{align*}
%       R(T)
%       &= \left(\sum_{k=1}^{M}\mu_k^*\right)T - \E_{\mu}\left[\sum_{t=1}^T\sum_{j=1}^M Y_{A^j(t),t} \eta^j(t) \right]
%        = \left(\sum_{k=1}^{M}\mu_k^*\right)T - \E_{\mu}\left[\sum_{t=1}^T\sum_{j=1}^M \mu_{A^j(t)} \eta^j(t)\right]
%       \intertext{The last equality comes from the linearity of expectations, and the fact that $\E_{\mu}[Y_{k,t}] = \mu_k$ (for all $t$, from the \iid{} hypothesis), and the independence from $A^j(t)$, $\eta^j(t)$ and $Y_{k,t}$ (observed \emph{after} playing $A^j(t)$). So $\E_{\mu}[Y_{A^j(t),t} \eta^j(t)] = \sum_{k} \E_{\mu}[\mu_k \indic(A^j(t),t) \eta^j(t)] = \E_{\mu}[\mu_{A^j(t)} \eta^j(t)]$. And so}
%       R(T)
%       &= \E_{\mu}\left[ \sum_{t=1}^{T}\sum_{j \in \Mbest} \mu_j
%         - \sum_{t=1}^{T} \sum_{j=1}^{M} \mu_{A^j(t)} \eta^j(t) \right] \\
%         % &= \underbrace{\left( \frac{1}{M} \sum_{j \in \Mbest} \mu_j \right)}_{:= \overline{\mu}^*} (T M)
%       &= \left( \frac{1}{M} \sum_{j \in \Mbest} \mu_j \right)
%         - \sum_{k=1}^{K} \sum_{j=1}^{M} \mu_k \E_{\mu}\left[ T^j_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
%       \intertext{For the first term, we have $T M = \sum\limits_{k=1}^{K} \sum\limits_{j=1}^{M} \E_{\mu}\left[ T^j_k(T)\right]$, and if we denote $\overline{\mu}^* := \frac{1}{M} \sum\limits_{j \in \Mbest} \mu_j$ the average mean of the $M$-best arms, then,}
%       &= \sum_{k=1}^{K} \sum_{j=1}^{M} (\overline{\mu}^* - \mu_k) \E_{\mu}\left[ T^j_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
%       \intertext{Let $\overline{\Delta_k} := \overline{\mu}^* - \mu_k$ be the gap between the mean of the arm $k$ and the $M$-best average mean, and if $M^*$ denotes the index of the worst of the $M$-best arms (\ie, $M^* = \arg\min_{k\in\Mbest}(\mu_k)$), then by splitting $\{1,\dots,K\}$ into three disjoint sets $\Mbest \cupdot \Mworst = (\Mbest\setminus\{M^*\}) \cupdot \{M^*\} \cupdot \Mworst$, we get}
%       &= \sum_{k \in \Mbest\setminus\{M\}} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]
%         + \overline{\Delta_{M^*}} \E_{\mu}\left[ T_{M^*}(T) \right] \\
%         &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
%       \intertext{But for $k = M^*$, $T_{M^*}(T) = T M^* - \sum\limits_{k \in \Mbest\setminus\{M\}} \E_{\mu}\left[ T_k(T) \right] - \sum\limits_{k \in \Mworst} \E_{\mu}\left[ T_k(T) \right]$, so by recombining the terms, we obtain,}
%       &= \sum_{k \in \Mbest\setminus\{M\}} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]
%         + \overline{\Delta_{M^*}} T M^* \\
%         &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
%     \end{align*}
%     The term $\overline{\Delta_k} - \overline{\Delta_{M^*}}$ simplifies to $\mu_{M^*} - \mu_k$, and so $\overline{\Delta_{M^*}} = \frac{1}{M} \sum_{k=1}^{M} \mu_k - \mu_{M^*}$ by definition of $\overline{\mu}^*$. And for $k=M^*$, $\mu_{M^*} - \mu_k = 0$, so the first sum can be written for $k = 1,\dots,M$ only, so
%     % \vspace*{5pt}
%     \begin{align*}
%       R(T)
%       &= \sum_{k \in \Mbest} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
%         + \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) T \\
%         &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right]
%     \end{align*}
%     And so we obtain the decomposition with three terms \ref{eq:5:term1}, \ref{eq:5:term2} and \ref{eq:5:term3}.
%     \begin{align*}
%     R(T)
%       &= \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) \left(T - \E_{\mu}\left[ T_k(T) \right]\right)
%         + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]
%         + \sum_{k=1}^{K} \mu_k \E_{\mu}\left[ \cC_k(T) \right].
%     \end{align*}
%     % Which is exactly the decomposition we wanted to prove.

% % -----------------------------------------------------------------
% \subsection{Proof of Lemma~\ref{lem:5:1stLowerBound}}
% \label{proof:5:1stLowerBound}

%   Note that term \ref{eq:5:term3} is clearly lower bounded by $0$
%   but it is not obvious for \ref{eq:5:term2} as there is no reason for $T_k(T)$ to be upper bounded by $T$.
%   %
%   Let $T_k^{!}(T) := \sum_{t=1}^{T} \indic(\exists! j, A^j(t)=k)$,
%   where the notation $\exists!$ stands for ``there exists a unique''.
%   Then $T_k(T) = \sum_{t=1}^{T} \sum_{j=1}^{M} \indic(A^j(t) = k)$ can be decomposed as
%   \begin{equation*}
%     T_k(T) = \sum_{t=1}^{T} \indic(\exists! j, A^j(t) = k) + \sum_{t=1}^{T} \sum_{j=1}^{M} c_{k,t} \indic(A^j(t) = k)
%     = T_k^{!}(T) + C_k(T).
%   \end{equation*}
%   By focusing on the two terms $\ref{eq:5:term2} + \ref{eq:5:term3}$ from the decomposition of $R_T(\boldsymbol{\mu}, M, \rho)$ from Lemma~\ref{lem:5:DecompositionRegret}, we have
%   \begin{align*}
%     \ref{eq:5:term2} + \ref{eq:5:term3} &=
%     \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
%     + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)] \\
%     & \;\;\;\;\;\; + \sum_{k=1}^{M} \mu_k \E_{\mu}[C_k(T)]
%     - \sum_{k \in \Mbest} \mu_k \E_{\mu}[C_k(T)] \\
%     &=
%     \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
%     + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)]
%     + \sum_{k \in \Mworst} \mu_k \E_{\mu}[C_k(T)] \\
%     &=
%     \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
%     + \sum_{k=1}^{M} \min(\mu_M^*, \mu_k) \E_{\mu}[C_k(T)].
%   \end{align*}
%   And now both terms are non-negative, as $T_k^!(T) \leq T$, $\min(\mu_M^*, \mu_k)\geq 0$, and $C_k(T) \geq 0$, so $\ref{eq:5:term2} + \ref{eq:5:term3} \geq 0$
%   which proves that $R_T(\boldsymbol{\mu}, M, \rho) \geq \ref{eq:5:term1}$, as wanted.

% % -----------------------------------------------------------------
% \subsection{Proof of Lemma~\ref{lem:5:1stUpperBound}}
% \label{proof:5:1stUpperBound}

% Recall that we want to upper bound
% $ (b) : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[T_k(T)]\right)$.
% First, we observe that, for all $k\in \Mbest$,
% \begin{eqnarray*}
%   T - \E_{\mu}[T_k(T)] & \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] \\
%   & = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],
% \end{eqnarray*}
% where we denote by $\widehat{S}_t = \{A^j(t), j \in \{1,\dots,M\}\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
% \begin{eqnarray*}
%  (b) & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[T_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
%  & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
% \end{eqnarray*}
% The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
% \[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
% which yields
% \[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[T_k(T)\right]\]
% and Lemma~\ref{lem:5:1stUpperBound} follows.

@@

@@

Using \eqref{eq:5:KeyInclusion}, one can then upper bound the number of selections of arm $k$ by user $j$ up to round $T$ as
\begin{align*}
\E_{\mu}[T_k^j(T)]
&= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
= \sum_{t=1}^T \Pr\left( A^j(t) = k \right).\\
%&= \sum_{t=1}^T \Pr\left( A^j(t) = k,\;\; \exists m \in\Mbest,\; g_m(t) < g_k(t) \right) \\
&= \sum_{t=1}^T \Pr\left( A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}^j(t) < g_k^j(t) \right).
%
\intertext{Considering the relative position of the upper-confidence bound $g_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition}
\E_{\mu}[T_k^j(T)] &\leq \sum_{t=1}^T\Pr\left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}(t) \leq g_k(t) , \forall m \in \{1,\dots,M\}: \;  g_{m^*}(t) \geq \mu_m^* \right)\\
&\;\;\;\;\;\;\;\; + \sum_{t=1}^T\Pr\left( \exists m \in\{1,\dots,M\}: \; g_{m^*}(t) < \mu_m^* \right) \\
&\leq \sum_{t=1}^T\Pr\left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; \mu_{m}^* \leq g_k(t)\right)+ \sum_{m=1}^M\sum_{t=1}^T\Pr\left(g_{m^*}(t) < \mu_m^* \right) \\
%
&\leq
\sum_{t=1}^T
  \Pr\left( A^j(t) = k,\; \mu_{M^*} \leq g_k(t) \right)
+
\sum_{m=1}^M
  \sum_{t=1}^T \Pr\left( g_{m^*}(t) < \mu_m^* \right),
\end{align*}
where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in \{1, \dots,M\}$.

### 2019-04-04 2-Chapters/5-Chapter/chapter5.tex
Moved a lot of appendix in main text for Chapter 5. See #15

Finally, another interesting extension is to consider different channels utility for each devices. It is a very interesting extension of our model, for instance the devices can be located on different parts of a building or a field and suffer from different mean qualities of access to each channels.
This extension is not studied per say but we quickly review the existing literature \cite{Bistritz18,KaufmannAbbas19} and discuss the possible real-world usage of the existing algorithms.

\TODOL{Get bibtex of the article by Sumit J. Darak}

@@

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter~\ref{chapter:5}}
\label{sec:5:conclusion}

@@

% ----------------------------------------------------------------------------
\section{Appendix for Chapter~\ref{chapter:5}}
\label{sec:5:appendix}

>>>>

Finally, another interesting extension of the studied models is to consider different channels utility for each devices. It is a very interesting extension of our model, as for instance the devices could be located on different parts of a building or a field and suffer from different mean qualities of access to each channels.
This extension is not studied per say but we quickly review the existing literature, consisting in the two recent works \cite{Bistritz18,KaufmannAbbas19}, and we discuss the possible real-world usage of the existing algorithms.

\TODOL{Get bibtex of the articles by Sumit J. Darak, and talk correctly about them!}

\vfill{}

\paragraph{Publications}

This chapter is mainly based on the following publication: \cite{Besson2018ALT}.

@@

% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:5:conclusion}

@@

% ----------------------------------------------------------------------------
\section{Appendix}
\label{sec:5:appendix}
